Towards a Mechanized Proof of Noninterference

### 2013-12-17 paper/paper.tex
Whoops, fixed bibtex reference.

\section{Introduction}
Introduce idea and outline what it will require us to do.  Explain where we're
starting from (Pottier and Simonet) at a high level.  Justify why this is an
interesting problem that needs tackling.

\section{Operational Semantics}
Outline the operational semantics of the baby language we developed.  Outline
any interesting similarities or differences between us and Pottier and Simonet.

\section{Type System}
Outline the type system of the language and again compare/contrast with
Pottier and Simonet.

@@

\section{Future Work}
Talk about stuff we still have to do for this to be a complete project.  Talk
about expected problems and required techniques.  Talk about what we could do
once this project is completed and we could use it for other projects.

\section{Conclusion}
Summarize again what we covered, where we ended up, and where we'd like to go
next.

\bibliographystyle{abbrv}
\bibliography{proposal.bib}
\section*{Acknowledgements}

Acknowledge people who really helped.  Primary name that comes to mind is that
nice Jon fellow we spent many hours on the phone getting advice from.
\end{document}

>>>>

\section{Introduction}

Introduce idea and outline what it will require us to do.  Explain where we're
starting from (Pottier and Simonet) at a high level.  Justify why this is an
interesting problem that needs tackling.

\section{Operational Semantics}

Outline the operational semantics of the baby language we developed.  Outline
any interesting similarities or differences between us and Pottier and Simonet.

\section{Type System}

Outline the type system of the language and again compare/contrast with
Pottier and Simonet.

@@

\section{Future Work}

Talk about stuff we still have to do for this to be a complete project.  Talk
about expected problems and required techniques.  Talk about what we could do
once this project is completed and we could use it for other projects.

\section{Conclusion}

Summarize again what we covered, where we ended up, and where we'd like to go
next.

\section*{Acknowledgements}

Acknowledge people who really helped.  Primary name that comes to mind is that
nice Jon fellow we spent many hours on the phone getting advice from.

\bibliographystyle{abbrv}
\bibliography{paper.bib}

\end{document}
